### 2010-02-11 doc/manuals/user_interface/ui-data.tex
arccp -f can be used to skip validation checks

\texttt{arccp}\index{arccp}\index{commands:arccp} is a powerful
tool to copy files over the Grid. It is a part of the A-REX,
but can be used by the User Interface as well.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccp [options] $<$source$>$ $<$destination$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
   \texttt{-p, --passive} && use passive transfer (does not work if secure is on, default if secure is not requested)\\
   \texttt{-n, --nopassive} && do not try to force passive transfer\\
   \texttt{-f, --force} && if the destination is an indexing service and not the same as the source and the destination is already registered, then the copy is normally not done. However, if this option is specified the source is assumed to be a replica of the destination created in an uncontrolled way and the copy is done like in case of replication\\
   \texttt{-i, --indicate} && show progress indicator\\
   \texttt{-T, --notransfer} && do not transfer file, just register it - destination must be non-existing meta-url\\
   \texttt{-u, --secure} && use secure transfer (insecure by default)\\
   \texttt{-y, --cache} &\textit{path} & path to local cache (use to put file into cache). The \texttt{X509\_USER\_PROXY} and \texttt{X509\_CERT\_DIR} environment variables must be set correctly\\
   \texttt{-r, --recursive} & \textit{recursion\_level} & operate recursively (if possible) up to specified level (0 - no recursion)\\
   \texttt{-R, --retries} & \textit{number} & how many times to retry transfer of every file before failing\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, VERBOSE or DEBUG - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
    Arguments:&&\\
    \texttt{source} && source URL\\
    \texttt{destination} && destination URL\\
\end{longtable}

>>>>

\texttt{arccp}\index{arccp}\index{commands:arccp} is a powerful
tool to copy files over the Grid. It is a part of the A-REX,
but can be used by the User Interface as well.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccp [options] $<$source$>$ $<$destination$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
   \texttt{-p, --passive} && use passive transfer (does not work if secure is on, default if secure is not requested)\\
   \texttt{-n, --nopassive} && do not try to force passive transfer\\
   \texttt{-f, --force} && if the destination is an indexing service and not the same as the source and the destination is already registered, then the copy is normally not done. However, if this option is specified the source is assumed to be a replica of the destination created in an uncontrolled way and the copy is done like in case of replication. Using this option also skips validation of completed transfers.\\
   \texttt{-i, --indicate} && show progress indicator\\
   \texttt{-T, --notransfer} && do not transfer file, just register it - destination must be non-existing meta-url\\
   \texttt{-u, --secure} && use secure transfer (insecure by default)\\
   \texttt{-y, --cache} &\textit{path} & path to local cache (use to put file into cache). The \texttt{X509\_USER\_PROXY} and \texttt{X509\_CERT\_DIR} environment variables must be set correctly\\
   \texttt{-r, --recursive} & \textit{recursion\_level} & operate recursively (if possible) up to specified level (0 - no recursion)\\
   \texttt{-R, --retries} & \textit{number} & how many times to retry transfer of every file before failing\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, VERBOSE or DEBUG - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
    Arguments:&&\\
    \texttt{source} && source URL\\
    \texttt{destination} && destination URL\\
\end{longtable}
